
---
title: "Skript X"
author: "dssrttn"
date: "2020-07-10"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(dev=c('png', 'pdf'), width=7, height=5)

```


```{r DIL mean for boxplot, message=FALSE, warning=FALSE}
library(plyr)
library(tidyverse)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
library(psych)
library(here)
library(jtools) # for linear regression output. not used so far
#options(digits=3) # zeigt nur drei Zahlenwerte an
source("code/plottheme.R")
source("code/cbPalette.R")



#DIL<- read_csv2('data/x/DIL.csv')
#Boost <- read_csv2('data/24/Boost.csv')
#Rectum <- read_csv2('data/24/Rectum.csv')
#Bladder <- read_csv2('data/24/Bladder.csv')
#XVI <- read_csv2('data/24/XVI.csv')
```
 




```{r scripting all files, message=FALSE, warning=FALSE}
files <- list.files(pattern="*.csv")

for (i in seq_along(files)){
  assign(files[i], read.csv(files[i]))
  <do something>
  write.csv(files[i], paste0("new_", files[i]), sep = ",")
}

```





read.csv expects to read just one file, so you need to loop over files, a R idiomatic way of doing so is to use sapply:

nrows <- sapply( csvfile, function(f) nrow(read.csv(f)) )
sum(nrows)

For example, here is a rewrite of your complete function:

complete <- function(directory,id = 1:332) {
    csvfiles <- sprintf("/Users/gcameron/Desktop/%s/%03d.csv", directory, id)
    nrows <- sapply( csvfiles, function(f) nrow(read.csv(f)) )
    sum(nrows)
}

