---
title: "Alles in einem"
author: "Mein Vorname"
date: "2020-07-10"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, message=FALSE}

knitr::opts_chunk$set(dev=c('png', 'pdf'), width=7, height=5)

```


```{r DIL mean for boxplot, message=FALSE}
library(plyr)
library(tidyverse)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
library(here)
#options(digits=3) # zeigt nur drei Zahlenwerte an
source("code/plottheme.R")
source("code/cbPalette.R")



DIL<- read_csv2('data/1/DIL.csv')
Boost <- read_csv2('data/1/Boost.csv')
```

## Relation of DIL and boost

### DIL[n] to boost[1] - boxplot with percentage relation

```{r DIL Boxplot, message=FALSE}

source(here::here("code/Boxplot_DIL_mean.R"))
#source(here::here("code/Boxplot_DIL_minus_Boost_mean.R"))
```

### DIL[n] to boost[1] - table with percentage relation

```{r DIL to Boost table, message=FALSE}
DIL_Boost_mean_relation %>%
 knitr::kable(format ='html', caption = "", col.names = c("DIL to boost relation relative to the first fraction", "Numbers")) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

```

### DIL minus boost - boxplot with percentage relation

```{r DIL minus boost Boxplot, message=FALSE}

source(here::here("code/Boxplot_DIL_minus_Boost_mean.R"))
```

### DIL minus boost - table with percentage relation

```{r DIL minus Boost table, message=FALSE}
DIL_minus_Boost_mean_table %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL minus boost", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```


## DIL and boost changes during the treatment period

### DIL changes relative to the first fraction

```{r Relative dose changes in percent for DIL, message=FALSE}




source("code/DILrelchange.R")

DIL_mean_rel_table %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html' #, caption = "DIL descriptive statistics"
        ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE)

```

### Boost changes relative to the first fraction

```{r Relative dose changes in percent for boost, message=FALSE}

source("code/Boostrelchange.R")
 
Boost_mean_rel_table %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html' #, caption = "Boost descriptive statistics"
        ) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
    full_width = TRUE) 

```

### Line plot for DIL and boost mean changes relative to the first fraction


```{r Relative dose changes DIL und boost in percent line plot, message = FALSE}

ggplot() + 
  geom_line(data = DIL_mean_rel_table, aes(x = 1:14, y = DIL_mean_rel$relchange, color = "DIL")) +
  geom_line(data = Boost_mean_rel_table , aes(x = 1:14, y = Boost_mean_rel$relchange, color = "Boost")) +
 geom_point(data = DIL_mean_rel_table, aes(x = 1:14, y = DIL_mean_rel$relchange, color = "DIL")) +
  geom_point(data = Boost_mean_rel_table , aes(x = 1:14, y = Boost_mean_rel$relchange, color = "Boost")) +
      scale_colour_manual(values=cbPalette) +  # To use for line and point colors, add
   expand_limits(y = c(-2, 2)) +
  scale_y_continuous(breaks = seq(-2, 2, 1.0), labels=function(x) paste0(x,"%")) + #labels=function(x) paste0(x,"%") adds percent symbol, but without multiplying it with 100, like when one does: scale_y_continuous(labels = scales::percent)
    scale_x_continuous(breaks = c(1,5,10,14))  + # adds only specific ticks
      geom_abline(intercept = 0, slope = 0, lty=2) + # horizontale Linie ohne Steigung, da slope = 0 
  ggtitle("DIL - Relative dose changes in percent from the 1st fraction with DIL") +
  xlab("Fraction") + # X-Achsen-Beschriftung
  ylab("Relative dose changes") +   #+ # Y-Achsen-Beschriftung
  plottheme

```


### Histogram for DIL mean changes relative to the first fraction


```{r DIL histogramm relative change, message=FALSE}
source("code/HistogramDILrelchange.R")

par(family="serif") # Schriftart
par(mar = c(5, 5, 2, 2)) # Abstände um den Plot. 2. Po´ition y-Achse
par(mgp=c(3,1,0)) # mpg: Abstand Label zu Achse
hist(HistogramDILrelchange$relchange,
         main="",
    #DIL Mittelwert" 
     ylab="Density", xlab="Relative DIL dose change", mgp=c(3,1,0), las = 1, freq = FALSE, ylim=c(0, 2), #xlim=c(-1, 0.3),
    cex.lab=2, cex.axis=1.5, col = "transparent")
rug(jitter(HistogramDILrelchange$relchange))
lines(density(HistogramDILrelchange$relchange), col="black", lwd=2)

```

### Histogram for boost mean changes relative to the first fraction

```{r Boost histogramm relative change, message=FALSE}
source("code/HistogramBoostrelchange.R")

par(family="serif") # Schriftart
par(mar = c(5, 5, 2, 2)) # Abstände um den Plot. 2. Po´ition y-Achse
par(mgp=c(3,1,0)) # mpg: Abstand Label zu Achse
hist(HistogramBoostrelchange$relchange,
         main="",
    #DIL Mittelwert" 
     ylab="Density", xlab="Relative boost dose change", mgp=c(3,1,0), las = 1, freq = FALSE, ylim=c(0, 2), #xlim=c(-1, 0.3),
    cex.lab=2, cex.axis=1.5, col = "transparent")
rug(jitter(HistogramBoostrelchange$relchange))
lines(density(HistogramBoostrelchange$relchange), col="black", lwd=2)


  
```


