---
title: "First-Analysis"
output: 
  html_document:
    code_folding: hide
---

       

## Erste Analyse

Dies ist ein erster Versuch zur Durchführung meiner Dissertation mithilfe von workflowr und **markdown**. 

##### Zweite Analyse

This is an ~~R Markdown~~ document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a *document will be generated* that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:





```{r}

DIL_1 <- read.table('data/DIL_1.csv', header=TRUE, stringsAsFactors=FALSE, sep=";", dec=",", row.names="Dosisname")

summary(DIL_1)
str(DIL_1)


x <- (1:14)
y <- DIL_1$Mittelwert

y.sd <- DIL_1$sigma


var(DIL_1$Mittelwert)
```



## Including Plots
```{r, fig.width=10, fig.height=7, dev=c('png', 'pdf')}
plot(x, y, ylim=c(74, 80.2), xlab="Fraktion", family="serif", ylab="Dosis in Gray", family="serif", axes = FALSE, pch=16, cex=0.5, main="Dosisverteilung DIL Mittelwert 1")
text(x=13.4, y = 75.8, labels="Dosisvorgabe Boost", family="serif")> 
text(x=12.5, y = 80.2, labels="+5% Abweichung von Dosisvorgabe", family="serif")
axis(1, at=x, label=x, tick=F, family="serif")
arrows(x0=x, y0=y-y.sd, x1=x, y1=y+y.sd, code=3, angle=90, length=0.05)
abline(a=76,23, b=0, lty=2)
abline(a=80.04, b=0, lty=2)
axis(2, at=seq(74,81,0.5), tick=F, las=2, family="serif")
```

### Ein weiterer Unterpunkt
### Noch einer

Lorem ipsum

