---
title: "Patient 25"
author: "dssrttn"
date: "2020-08-20"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(dev=c('png', 'pdf'), width=7, height=5)

```


```{r DIL mean for boxplot, message=FALSE, warning=FALSE}
library(plyr)
library(tidyverse)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
library(psych)
library(broom)
library(here)
library(jtools) # for linear regression output. not used so far
options(digits=3) # zeigt nur drei Zahlenwerte an
source("code/plottheme.R")
source("code/cbPalette.R")
source("code/lineplottheme.R")
source("code/boxplottheme.R")

DIL<- read_csv2('data/25/DIL.csv')
Boost <- read_csv2('data/25/Boost.csv')
Rectum <- read_csv2('data/25/Rectum.csv')
Bladder <- read_csv2('data/25/Bladder.csv')
XVI <- read_csv2('data/25/XVI.csv')
```




# Dose
## DIL and boost changes during the treatment period

### DIL changes relative to the first fraction of DIL




```{r Relative dose changes in percent for DIL, message=FALSE}

source(here::here("code/DILrelchange.R"))
DIL_mean_rel_table %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html' #, caption = "DIL descriptive statistics"
        ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE)


```

### Lollipop plot for DIL mean changes relative to the first fraction of DIL


aes(x=1:nrow(speed1)

```{r Lollipop plot DIL relative change, message=FALSE}
source(here::here("code/Lollipopplot_DIL_mean.R"))

ggplot(DIL_mean_rel,aes(x=1:nrow(DIL_mean_rel) #DIL_relabs$x
                      ,y=y )) + #DIL_relabs$abschange)) +
geom_segment( aes(x=1:nrow(DIL_mean_rel), xend=1:nrow(DIL_mean_rel), y=0, yend=y), color="black") + # Striche von der Hoehe y bis zu den Punkten
geom_point() +
scale_x_continuous(breaks = c(1,5,10,nrow(DIL_mean_rel)))  + # adds only specific ticks
ggtitle("DIL - Relative dose changes in percent from the 1st fraction with DIL") +
xlab("Fraction") + # X-Achsen-Beschriftung
ylab("Relative dose changes") + # Y-Achsen-Beschriftung 
plottheme +
lineplottheme
    
```


### Boost changes relative to the first fraction of boost 

```{r Relative dose changes in percent for boost, message=FALSE}

source("code/Boostrelchange.R")
 
Boost_mean_rel_table %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html' #, caption = "Boost descriptive statistics"
        ) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
    full_width = TRUE) 

```

### Lollipop plot for Boost mean changes relative to the first fraction of Boost

```{r Lollipop plot Boost relative change, message=FALSE}
source(here::here("code/Lollipopplot_Boost_mean.R"))

ggplot(Boost_mean_rel,aes(x=1:nrow(Boost_mean_rel)
                        ,y=y )) +
geom_segment( aes(x=1:nrow(Boost_mean_rel), xend=1:nrow(Boost_mean_rel), y=0, yend=y), color="black") + # Striche von der Hoehe y bis zu den Punkten
geom_point() +
scale_x_continuous(breaks = c(1,5,10,nrow(Boost_mean_rel)))  + # adds only specific ticks
ggtitle("Boost - Relative dose changes in percent from the 1st fraction with Boost") +
xlab("Fraction") + # X-Achsen-Beschriftung
ylab("Relative dose changes") + # Y-Achsen-Beschriftung 
plottheme +
lineplottheme

```



### Line plot for DIL and boost mean changes relative to their respective first fraction
nrow(DIL_mean_rel)
aes(x=1:nrow(speed1)

```{r Relative dose changes DIL und boost in percent line plot, message = FALSE}

ggplot() + 
geom_line(data = DIL_mean_rel_table, aes(x = 1:nrow(DIL_mean_rel_table), y = DIL_mean_rel$relchange, color = "DIL")) +
geom_line(data = Boost_mean_rel_table , aes(x = 1:nrow(DIL_mean_rel_table), y = Boost_mean_rel$relchange, color = "Boost")) +
geom_point(data = DIL_mean_rel_table, aes(x = 1:nrow(DIL_mean_rel_table), y = DIL_mean_rel$relchange, color = "DIL")) +
geom_point(data = Boost_mean_rel_table , aes(x = 1:nrow(DIL_mean_rel_table), y = Boost_mean_rel$relchange, color = "Boost")) +
scale_colour_manual(values=cbPalette) +  # To use for line and point colors, add
scale_x_continuous(breaks = c(1,5,10,nrow(DIL_mean_rel_table)))  + # adds only specific ticks
ggtitle("DIL - Relative dose changes in percent from the 1st fraction with DIL") +
xlab("Fraction") + # X-Achsen-Beschriftung
ylab("Relative dose changes") +   #+ # Y-Achsen-Beschriftung
plottheme + 
lineplottheme

```



## Relation of DIL and boost

### DIL[n] to boost[1] - boxplot with percentage relation

(Mittelwert_DIL/ Mittelwert_Boost[1])

```{r DIL to Boost 1 Boxplot, message=FALSE}

source(here::here("code/Boxplot_to_DIL_1.R"))


```

### DIL[n] to boost[1] - table with percentage relation

(Mittelwert_DIL/ Mittelwert_Boost[1])

```{r DIL to Boost 1 table, message=FALSE}

DILtoBoost_1_mean_table %>%
 knitr::kable(format ='html', caption = "", col.names = c("DIL to boost relation relative to the first fraction", "Numbers")) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

```


### DIL[n] to boost[n] - boxplot with percentage relation

(Mittelwert_DIL/ Mittelwert_Boost[n])

```{r DIL to Boost n Boxplot, message=FALSE}

source(here::here("code/Boxplot_to_DIL_n.R"))



```


### DIL[n] to boost[n] - table with percentage relation

(Mittelwert_DIL[n]/ Mittelwert_Boost[n])

```{r DIL to Boost n table, message=FALSE}

DILtoBoost_n_mean_table %>%
 knitr::kable(format ='html', caption = "", col.names = c("DIL to boost relative relation", "Numbers")) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

```

### DIL[n] to boost[n] - table with 2 percent difference 

```{r DIL to Boost 2 percent dips table, message=FALSE}

source(here::here("code/DILtoBoostn_2percent.R"))


DILtoBoost_2percent_mean_table %>%
 knitr::kable(format ='html', caption = "", col.names = c("DIL to boost relative relation", "Numbers")) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

```



### DIL minus boost - boxplot with percentage relation

(Mittelwert_DIL-Mittelwert_Boost)/(Mittelwert_DIL[1]-Mittelwert_Boost[1]))

```{r DIL minus boost Boxplot, message=FALSE}

source(here::here("code/Boxplot_DIL_minus_Boost_mean.R"))



```

### DIL minus boost - table with percentage relation

(Mittelwert_DIL-Mittelwert_Boost)/(Mittelwert_DIL[1]-Mittelwert_Boost[1]))

```{r DIL minus Boost table, message=FALSE}

DIL_minus_Boost_mean_table %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL minus boost", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```


### Linear regression Boost mean DIL mean

```{r linear regression Boost DIL means,  width=7, height=5, dev=c('png', 'pdf'), message=FALSE}

plot(Boost_mean_rel$relchange, DIL_mean_rel$relchange)
x_Boost_mean_rel <- Boost_mean_rel$relchange
y_DIL_mean_rel <- DIL_mean_rel$relchange

linearregression_Boost_DIL <- lm(y_DIL_mean_rel ~ x_Boost_mean_rel)

lm(formula = y_DIL_mean_rel ~ x_Boost_mean_rel)

fitted.values(linearregression_Boost_DIL)
residuals(linearregression_Boost_DIL)

summary(linearregression_Boost_DIL)


plot(x_Boost_mean_rel, y_DIL_mean_rel)
abline(linearregression_Boost_DIL, col = "red")

#tidy(linearregression_Boost_DIL)

```



## Rectum
### Rectum changes relative to the first fraction of Rectum

```{r Relative dose changes in percent for rectum, message=FALSE}

source(here::here("code/Rectum_mean_rel.R"))


Rectum_mean_rel_table %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html', caption = "Rectum mean descriptive statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE)

```


### Lollipop plot for rectum mean changes relative to the first fraction of rectum

```{r Lollipop plot relative dose changes of rectum in percent, message = FALSE}
source(here::here("code/Rectum_mean_rel.R"))


ggplot(Rectum_mean_rel, aes(x=1:nrow(Rectum_mean_rel)
                            , y=y)) + 
geom_segment( aes(x=1:nrow(Rectum_mean_rel), xend=1:nrow(Rectum_mean_rel), y=0, yend=y), color="black") + # Striche von der Hoehe y bis zu den Punkten
geom_point() +
scale_x_continuous(breaks = c(1,5,10,nrow(Rectum_mean_rel)))  + # adds only specific ticks
ggtitle("DIL - Relative dose changes in percent from the 1st fraction") +
xlab("Fraction") + # X-Achsen-Beschriftung
ylab("Relative dose changes") +
plottheme + 
lineplottheme


```

## Linear regression rectum mean and DIL mean


```{r linear regression Rectum DIL means, message=FALSE}
plot(Rectum_mean_rel$relchange, DIL_mean_rel$relchange)

x_Rectum_mean_rel <- Rectum_mean_rel$relchange
y_DIL_mean_rel <- DIL_mean_rel$relchange

linearregression_rectum_DIL <- lm(y_DIL_mean_rel ~ x_Rectum_mean_rel)
lm(formula = y_DIL_mean_rel ~ x_Rectum_mean_rel)

fitted.values(linearregression_rectum_DIL)

residuals(linearregression_rectum_DIL)

summary(linearregression_rectum_DIL)

plot(x_Rectum_mean_rel, y_DIL_mean_rel)
abline(linearregression_rectum_DIL, col = "red")


```




## Bladder
### Bladder changes relative to the first fraction of bladder

```{r Relative dose changes in percent for bladder, message=FALSE}

source(here::here("code/Bladder_mean_rel.R"))
 

Bladder_mean_rel_table %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html', caption = "Rectum mean descriptive statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE)

```


### Lollipop plot for bladder mean changes relative to the first fraction of bladder

```{r Lollipop plot relative dose changes of bladder in percent, message = FALSE}
source(here::here("code/Bladder_mean_rel.R"))


ggplot(Bladder_mean_rel, aes(x=1:nrow(Bladder_mean_rel), y=y)) + 
 geom_segment( aes(x=1:nrow(Bladder_mean_rel), xend=1:nrow(Bladder_mean_rel), y=0, yend=y), color="black") + # Striche von der Hoehe y bis zu den Punkten
geom_point() +
scale_x_continuous(breaks = c(1,5,10,nrow(Bladder_mean_rel)))  + # adds only specific ticks
geom_abline(intercept = 0, slope = 0, lty=1, col='orange') + # horizontale Linie ohne Steigung, da slope = 0 
ggtitle("DIL - Relative dose changes in percent from the 1st fraction in rectum dvh") +
xlab("Fraction") + # X-Achsen-Beschriftung
ylab("Relative dose changes") +
plottheme + 
lineplottheme

```

## Relation bladder mean and DIL mean

```{r linear regression Bladder DIL means, message=FALSE}
#source(here::here("code/Bladder_mean_rel.R"))

plot(Bladder_mean_rel$relchange, DIL_mean_rel$relchange)

x_Bladder_mean_rel <- Bladder_mean_rel$relchange
y_DIL_mean_rel <- DIL_mean_rel$relchange

linearregression_Bladder_DIL <- lm(y_DIL_mean_rel ~ x_Bladder_mean_rel)
lm(formula = y_DIL_mean_rel ~ x_Bladder_mean_rel)

fitted.values(linearregression_Bladder_DIL)
residuals(linearregression_Bladder_DIL)

summary(linearregression_Bladder_DIL)


plot(x_Bladder_mean_rel, y_DIL_mean_rel)
abline(linearregression_Bladder_DIL, col = "red")


```


# Displacement relocation in cm

```{r XVI, message=FALSE, warning=FALSE}

source(here::here("code/XVI.R"))


XVI_tibble_date %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html', caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE)



XVI_tibble %>%
  kable(align = c("ccccccccc"), escape = FALSE, format ='html', caption = "") %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
    full_width = TRUE) 

```
