---
title: "All patients"
author: "dssrttn"
date: "2020-09-15"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(dev=c('png', 'pdf'), width=7, height=5)

```


```{r DIL mean for boxplot, message=FALSE, warning=FALSE}
library(plyr)
library(tidyverse)
library(ggplot2)
library(scales)
library(purrr)
library(knitr)
library(kableExtra)
library(psych)
library(broom)
library(here)
library(data.table)
library(metan)
library(jtools) # for linear regression output. not used so far
options(digits=3) # zeigt nur drei Zahlenwerte an
source("code/plottheme.R")
source("code/cbPalette.R")
source("code/lineplottheme.R")
source("code/boxplottheme.R")

```


# DIL and boost relations
## DIL and boost changes during the treatment period
```{r, message=FALSE}



all_folders <- list.dirs('data/stack', recursive = FALSE, full.names = TRUE)
result <- purrr::map_df(all_folders, function(x) {
  all_Files <- list.files(x, full.names = TRUE, pattern = 'DIL|Boost')
df1 <- read.csv2(all_Files[2])
df2 <- read.csv2(all_Files[1])
tibble::tibble(DIL = df1$Mittelwert, Boost = df2$Mittelwert, diltoboost = DIL/Boost, diltoboost_1 = DIL/Boost[1], dilminusboost =  (DIL-Boost)/(DIL[1]-Boost[1]))
}, .id = "id")
#result



result %>%
 knitr::kable(format ='html', caption = "", #col.names = c("DIL to boost relative relations", #"Numbers")
              ) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

countdiltoboost <- result

countdiltoboost_1 <- result

countdilminusboost <- result


write_csv(result,"~/Documents/RStudio/Test/Test/output/result.csv")

```


### DIL[n] to boost[n] - boxplot with percentage relation

(Mittelwert_DIL[n]/ Mittelwert_Boost[n])

```{r DIL to Boost, message=FALSE}

max <-max(result$diltoboost) # _1 für 1. Fraktion
min <-min(result$diltoboost)

par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(result$diltoboost,
        ylab= "DIL[n] to Boost[n]", #y-Achse-Beschriftung
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*min), max(1.005*max)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)



countdiltoboost <- cut(result$diltoboost, c(-Inf, 0.95, 0.96, 0.97, 0.98, 0.99, 1.00, 1.01, 1.02, 1.03, 1.04, 1.05, Inf), labels=c('<95%', '95-96%', '96-97%', '97-98%', '98-99%', '99-100%', '100-101%', '101-102%', '102-103%', '103-104%', '104-105%', '>105%'))  # benutzt dplyr, 7 Intervalle


countdiltoboost <- as.data.frame(countdiltoboost) %>%
  group_by(countdiltoboost, .drop = FALSE) %>% #.drop = FALSE ansonsten Fehlermeldung, weil  empty categories are dropped by default. You can change this behavior by adding .drop = FALSE
  dplyr::summarise(Numbers = n()) 


countdiltoboost %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL_n to Boost_n relation", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


write_csv(countdiltoboost,"~/Documents/RStudio/Test/Test/output/countdiltoboost.csv")


countdiltoboost_2percent <- cut(result$diltoboost, c(-Inf, 0.98, 1.02, Inf), labels=c('<98%', '98-102%', '>102%'))  # benutzt dplyr, 7 Intervalle

countdiltoboost_2percent <- as.data.frame(countdiltoboost_2percent) %>%
  group_by(countdiltoboost_2percent, .drop = FALSE) %>% #.drop = FALSE ansonsten Fehlermeldung, weil  empty categories are dropped by default. You can change this behavior by adding .drop = FALSE
  dplyr::summarise(Numbers = n())  #%>% # %>% #=n())
#mutate(Nummers = rowSums(.[-1]))


countdiltoboost_2percent %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL to boost", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)



write_csv(countdiltoboost_2percent,"~/Documents/RStudio/Test/Test/output/countdiltoboost_2percent.csv")



```



### DIL minus boost - boxplot with percentage relation

(Mittelwert_DIL-Mittelwert_Boost)/(Mittelwert_DIL[1]-Mittelwert_Boost[1]))

```{r DIL minus boost Boxplot, message=FALSE}

max <-max(result$dilminusboost) # _1 für 1. Fraktion
min <-min(result$dilminusboost)

par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(result$dilminusboost,
        ylab= "DIL[n] minus Boost[n]", #y-Achse-Beschriftung
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*min), max(1.005*max)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)




countdilminusboost<- cut(result$dilminusboost, c(-Inf, 0.95, 0.96, 0.97, 0.98, 0.99, 1.00, 1.01, 1.02, 1.03, 1.04, 1.05, Inf), labels=c('<95%', '95-96%', '96-97%', '97-98%', '98-99%', '99-100%', '100-101%', '101-102%', '102-103%', '103-104%', '104-105%', '>105%'))  # benutzt dplyr, 7 Intervalle

countdilminusboost <- as.data.frame(countdilminusboost) %>%
  group_by(countdilminusboost, .drop = FALSE) %>% #.drop = FALSE ansonsten Fehlermeldung, weil  empty categories are dropped by default. You can change this behavior by adding .drop = FALSE
  dplyr::summarise(Numbers = n()) 

countdilminusboost %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL minus Boost relation", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


write_csv(countdilminusboost,"~/Documents/RStudio/Test/Test/output/countdilminusboost.csv")

countdilminusboost2percent <- cut(result$dilminusboost, c(-Inf, 0.98, 1.02, Inf), labels=c('<98%', '98-102%', '>102%'))  # benutzt dplyr, 7 Intervalle

countdilminusboost2percent <- as.data.frame(countdilminusboost2percent) %>%
  group_by(countdilminusboost2percent, .drop = FALSE) %>% #.drop = FALSE ansonsten Fehlermeldung, weil  empty categories are dropped by default. You can change this behavior by adding .drop = FALSE
  dplyr::summarise(Numbers = n())  #%>% # %>% #=n())
#mutate(Nummers = rowSums(.[-1]))


countdilminusboost2percent %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL minus boost", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


write_csv(countdilminusboost2percent,"~/Documents/RStudio/Test/Test/output/countdilminusboost2percent.csv")


```




### DIL[n] to boost[1] - boxplot with percentage relation

(Mittelwert_DIL/ Mittelwert_Boost[1])

```{r DIL to Boost 1 Boxplot, message=FALSE}

max <-max(result$diltoboost_1) # _1 für 1. Fraktion
min <-min(result$diltoboost_1)

par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(result$diltoboost_1,
        ylab= "Tolle Beschrifung", #y-Achse-Beschriftung DIL[n] to Boost[1]
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*min), max(1.005*max)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)



countdiltoboost_1 <- cut(result$diltoboost_1, c(-Inf, 0.95, 0.96, 0.97, 0.98, 0.99, 1.00, 1.01, 1.02, 1.03, 1.04, 1.05, Inf), labels=c('<95%', '95-96%', '96-97%', '97-98%', '98-99%', '99-100%', '100-101%', '101-102%', '102-103%', '103-104%', '104-105%', '>105%'))  # benutzt dplyr, 7 Intervalle


countdiltoboost_1 <- as.data.frame(countdiltoboost_1) %>%
  group_by(countdiltoboost_1, .drop = FALSE) %>% #.drop = FALSE ansonsten Fehlermeldung, weil  empty categories are dropped by default. You can change this behavior by adding .drop = FALSE
  dplyr::summarise(Numbers = n()) 


countdiltoboost_1 %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL_n to Boost_1 relation", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


write_csv(countdiltoboost_1,"~/Documents/RStudio/Test/Test/output/countdiltoboost_1.csv")


countdiltoboost_1_2percent <- cut(result$diltoboost_1, c(-Inf, 0.98, 1.02, Inf), labels=c('<98%', '98-102%', '>102%'))  # benutzt dplyr, 7 Intervalle

countdiltoboost_1_2percent <- as.data.frame(countdiltoboost_1_2percent) %>%
  group_by(countdiltoboost_1_2percent, .drop = FALSE) %>% #.drop = FALSE ansonsten Fehlermeldung, weil  empty categories are dropped by default. You can change this behavior by adding .drop = FALSE
  dplyr::summarise(Numbers = n())  #%>% # %>% #=n())
#mutate(Nummers = rowSums(.[-1]))


countdiltoboost_1_2percent %>%
  knitr::kable(format ='html', caption = "", col.names = c("DIL to boost_1", "Numbers")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)



write_csv(countdiltoboost_1_2percent,"~/Documents/RStudio/Test/Test/output/countdiltoboost_1_2percent.csv")

```



```{r diltoboost, message=FALSE}


result$id <- factor(result$id, levels=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26))

boxplot(result$diltoboost ~ result$id) 


boxplot(result$diltoboost_1 ~ result$id) 


boxplot(result$dilminusboost ~ result$id) 


```


par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(result$diltoboost ~ result$id,
ylab= "DIL[n] to Boost[n]", #y-Achse-Beschriftung
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*min), max(1.005*max)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)


## Descriptive statistics DIL-boost relations 
´
```{r descriptive statistics, message=FALSE}

resulttable <- result

resulttable_desc_stat <-resulttable <- resulttable[ , -c(1:3)] # removing 1st to 3rd column in dataframe "resulttable"

resulttable_desc_stat <- metan::desc_stat(resulttable, stats = c("n, min, median, mean, max, range, iqr, q2.5, q25, q75, q97.5, ci, sd.amo")) 
resulttable_desc_stat <- resulttable_desc_stat  %>% rename(Numbers = n, Mean = mean, 'Standard deviation' = sd.amo, Median = median, Minimum = min, 'Interquartile range' = iqr, 'Percentile 2.5' = q2.5, Quartile = q25, 'Third quartile' = q75, 'Percentile 97.5' = q97.5, Maximum = max, Range = range, '95 percent confidence interval of the mean' = ci)

                                          
write_csv(resulttable_desc_stat,"~/Documents/RStudio/Test/Test/output/resulttable_desc_stat.csv")


resulttable_desc_stat %>%
  kable(align = c("cccccccc"),'html') %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) # %>%



```

# Rectum

```{r Rectum, message=FALSE}



all_folders <- list.dirs('data/stack', recursive = FALSE, full.names = TRUE)
rectumresult <- purrr::map_df(all_folders, function(x) {
  all_Files <- list.files(x, full.names = TRUE, pattern = 'Rectum')
df1 <- read.csv2(all_Files[1])
#df2 <- read.csv2(all_Files[1])
tibble::tibble(rectum = df1$Mittelwert, rectumtorectum_1 = rectum/rectum[1])
}, .id = "id")
#result


rectumresult %>%
 knitr::kable(format ='html', caption = "", #col.names = c("Rectum to rectum relations", #"Numbers")
              ) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

rectumresulttable <- rectumresult


```


## Descriptive statistics rectum-rectum[1] relations 


```{r Descriptive statistics rectum-rectum[1], message=FALSE}

#rectumresulttable_desc_stat <-rectumresulttable <- rectumresulttable[ , -c(1:3)] # removing 1st to 3rd column in dataframe "resulttable"

rectumresulttable_desc_stat <- metan::desc_stat(rectumresulttable, stats = c("n, min, median, mean, max, range, iqr, q2.5, q25, q75, q97.5, ci, sd.amo")) 
rectumresulttable_desc_stat <- rectumresulttable_desc_stat  %>% rename(Numbers = n, Mean = mean, 'Standard deviation' = sd.amo, Median = median, Minimum = min, 'Interquartile range' = iqr, 'Percentile 2.5' = q2.5, Quartile = q25, 'Third quartile' = q75, 'Percentile 97.5' = q97.5, Maximum = max, Range = range, '95 percent confidence interval of the mean' = ci)

                                          
write_csv(rectumresulttable_desc_stat,"~/Documents/RStudio/Test/Test/output/rectumresulttable_desc_stat.csv")


rectumresulttable_desc_stat %>%
  kable(align = c("cccccccc"),'html') %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) # %>%

maxrectum <-max(rectumresult$rectumtorectum_1) 
minrectum <-min(rectumresult$rectumtorectum_1)

par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(rectumresult$rectumtorectum_1,
        ylab= "Rectum[n] to Rectum[1]", #y-Achse-Beschriftung
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*minrectum), max(1.005*maxrectum)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)



```


par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(rectumresult$rectumtorectum_1 ~ result$id,
        ylab= "Rectum[n] to Rectum[1]", #y-Achse-Beschriftung
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*min), max(1.005*max)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)


# Bladder

```{r Bladder, message=FALSE}



all_folders <- list.dirs('data/stack', recursive = FALSE, full.names = TRUE)
bladderresult <- purrr::map_df(all_folders, function(x) {
  all_Files <- list.files(x, full.names = TRUE, pattern = 'Bladder')
  df1 <- read.csv2(all_Files[1])
  #df2 <- read.csv2(all_Files[1])
  tibble::tibble(bladder = df1$Mittelwert, bladdertobladder_1 = bladder/bladder[1])
}, .id = "id")
#result


bladderresult %>%
  knitr::kable(format ='html', caption = "", #col.names = c("bladder to bladder relations", #"Numbers")
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 

bladderresulttable <- bladderresult

```

## Descriptive statistics bladder-bladder[1] relations 


```{r Descriptive statistics bladder-bladder[1], message=FALSE}

#bladderresulttable_desc_stat <-bladderresulttable <- bladderresulttable[ , -c(1:3)] # removing 1st to 3rd column in dataframe "resulttable"

bladderresulttable_desc_stat <- metan::desc_stat(bladderresulttable, stats = c("n, min, median, mean, max, range, iqr, q2.5, q25, q75, q97.5, ci, sd.amo")) 
bladderresulttable_desc_stat <- bladderresulttable_desc_stat  %>% rename(Numbers = n, Mean = mean, 'Standard deviation' = sd.amo, Median = median, Minimum = min, 'Interquartile range' = iqr, 'Percentile 2.5' = q2.5, Quartile = q25, 'Third quartile' = q75, 'Percentile 97.5' = q97.5, Maximum = max, Range = range, '95 percent confidence interval of the mean' = ci)


write_csv(bladderresulttable_desc_stat,"~/Documents/RStudio/Test/Test/output/bladderresulttable_desc_stat.csv")


bladderresulttable_desc_stat %>%
  kable(align = c("cccccccc"),'html') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) # %>%



maxbladder <-max(bladderresult$bladdertobladder_1) 
minbladder <-min(bladderresult$bladdertobladder_1)

par(bty="n") # keinen Rahmen
par(family="serif") # Schriftart
par(mar = c(2, 6.5, 2, 2)) # Abstände um den Plot. 2. Position y-Achse
par(mgp=c(5,1,0)) # mpg: Abstand Label zu Achse
boxplot(bladderresult$bladdertobladder_1,
        ylab= "bladder[n] to bladder[1]", #y-Achse-Beschriftung
        #yaxt="n", #suppresses y-axis. Brauch ich das?
        col="transparent", #Farbe des Boxplots
        las = 2, # horizontale Markierung der Tick-Beschriftungen
        #ylim = c(0, 1),
        ylim=c(min(0.995*minbladder), max(1.005*maxbladder)), # y-Achse range
        cex.lab = 2, # Größe Label-Beschriftung
        cex.axis = 1.5, # Größe Achsenbeschriftungen
        mgp=c(2.5,0.2,0) # mpg: Abstand Label zu Achse
        # , xpd = TRUE
        #labels = FALSE
)




```





#countdiltoboost <- result
#
#countdiltoboost_1 <- result
##countdilminusboost <- result


write_csv(result,"~/Documents/RStudio/Test/Test/output/rectumresult.csv")
