---
title: "data from all"
author: "dssrttn"
date: "2020-07-10"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r setup, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(dev=c('png', 'pdf'), width=7, height=5)

```


```{r DIL mean for boxplot, message=FALSE, warning=FALSE}
library(plyr)
library(tidyverse)
library(ggplot2)
library(scales)
library(purrr)
library(knitr)
library(kableExtra)
library(psych)
library(broom)
library(here)
library(data.table)
library(jtools) # for linear regression output. not used so far
options(digits=3) # zeigt nur drei Zahlenwerte an
source("code/plottheme.R")
source("code/cbPalette.R")
source("code/lineplottheme.R")
source("code/boxplottheme.R")

DIL<- read_csv2('data/1/DIL.csv')
Boost <- read_csv2('data/1/Boost.csv')
Rectum <- read_csv2('data/1/Rectum.csv')
Bladder <- read_csv2('data/1/Bladder.csv')
XVI <- read_csv2('data/1/XVI.csv')
```

```{r, message=FALSE}



all_folders <- list.dirs('data/stack', recursive = FALSE, full.names = TRUE)
result <- purrr::map_df(all_folders, function(x) {
  all_Files <- list.files(x, full.names = TRUE, pattern = 'DIL|Boost')
df1 <- read.csv2(all_Files[1])
df2 <- read.csv2(all_Files[2])
tibble::tibble(DIL = df1$Mittelwert, Boost = df2$Mittelwert, diltoboost = DIL/Boost)
}, .id = "id")
result



result %>%
 knitr::kable(format ='html', caption = "", #col.names = c("DIL to boost relative relations", #"Numbers")
              ) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) 
``` 


df3 <- read.csv2(all_Files[3])
df4 <- read.csv2(all_Files[4])
df5 <- read.csv2(all_Files[5])
df6 <- read.csv2(all_Files[6])
df7 <- read.csv2(all_Files[7])
df8 <- read.csv2(all_Files[8])
df9 <- read.csv2(all_Files[9])
df10 <- read.csv2(all_Files[10])
df11 <- read.csv2(all_Files[11])
#df12 <- read.csv2(all_Files[12])
df13 <- read.csv2(all_Files[13])
df14 <- read.csv2(all_Files[14])
df15 <- read.csv2(all_Files[15])
df16 <- read.csv2(all_Files[16])
df17 <- read.csv2(all_Files[17])
df18 <- read.csv2(all_Files[18])
df19 <- read.csv2(all_Files[19])
df20 <- read.csv2(all_Files[20])
df21 <- read.csv2(all_Files[21])
df22 <- read.csv2(all_Files[22])
df23 <- read.csv2(all_Files[23])
df24 <- read.csv2(all_Files[24])
df25 <- read.csv2(all_Files[25])
df26 <- read.csv2(all_Files[26])
